---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
```

# `r #metad$toc$sec1$nmn`

 Ed. Solomon

> "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**. 


## `r metad$toc$sec1$unm[1]`


- Two candidates: A, B
- County with three precincts: 1, 2, 3
- Two modes of voting
  - Number of ballots mode 1: S, T
  - Number of ballots mode 2: U, V



##

```{r, echo=F, caption="Example 1"}
## Tower 1
ex1m <- as.matrix(cbind(S,T,U,V))
towi <- as.data.frame(ex1m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))

towi[3:4,1] <- ""
towi[4,2] <- ""
lego_hux_nor_i <- hux(towi[,1:3]) 
lego_hux_nor_i 
```

```{r, echo=F, caption="Example 2"}
## Tower 2
ex2m <- as.matrix(cbind(S,T,Up,Vp))
towii <- as.data.frame(ex2m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))
towii[3:4,1] <- ""
towii[4,2] <- ""
lego_hux_nor_ii <- hux(towii[,1:3]) 
lego_hux_nor_ii 
```


## `r metad$toc$sec1$unm[2]`

```{r, echo=F}
lego_hux_nor <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
  set_background_color(1, 1:2, "black") %>% 
  set_background_color(2, 1:2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_nor %>% set_caption("")
```


Parameters: ** $x$, $y$, $\zeta$, $\alpha$, $\lambda$ **
\begin{equation*}
x=`r modlat$x_s[1]` \text{, }y=`r modlat$y_s[1]`
\end{equation*}
\begin{equation*}
\zeta=`r modlat$zeta_s[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lamda_s[1]`=`r modlat$lamda_s[2]`
\end{equation*}

##



```{r, echo=F}
ctone_sf <- 'Election results applying standard form on case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

Numerical calculation of candidate one total percentage
- Precinct 1
 - $\alpha=\frac{`r cx[1]`+`r cy[1]`\cdot `r czeta[1]`}{1+`r czeta[1]`}=`r calpha[1]`$
- Precinct 2
 - $\alpha=\frac{`r cx[2]`+`r cy[2]`\cdot `r czeta[2]`}{1+`r czeta[2]`}=`r calpha[2]`$
- Precinct 3
 - $\alpha=\frac{`r cx[3]`+`r cy[3]`\cdot `r czeta[3]`}{1+`r czeta[3]`}=`r calpha[3]`$

## `r metad$toc$sec1$unm[3]`

```{r, echo=F}
lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(1:2, 1, "black") %>% 
  set_background_color(1:2, 2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_imp %>% set_caption("")
```

Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
\begin{equation*}
g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
\end{equation*}

##

```{r, echo=F}
ctone_hf <- 'Election results applying hybrid form case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

Numerical calculation of candidate one total percentage
- Precinct 1
 - $\alpha=\frac{`r cg[1]`+`r ch[1]`\cdot `r cGamma[1]`}{1+`r cGamma[1]`}=`r calpha[1]`$
- Precinct 2
 - $\alpha=\frac{`r cg[2]`+`r ch[2]`\cdot `r cGamma[2]`}{1+`r cGamma[2]`}=`r calpha[2]`$
- Precinct 3
 - $\alpha=\frac{`r cg[3]`+`r ch[3]`\cdot `r cGamma[3]`}{1+`r cGamma[3]`}=`r calpha[3]`$

```{r, echo=F}
ctone_hf <- 'Election results applying hybrid form case II'
stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```



## `r metad$toc$sec1$unm[4]`

```{r, echo=F}
lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(c(1),c(1), "black") %>% 
  set_background_color(c(2),c(2), "black") %>% 
  set_background_color(c(1),c(2), "grey") %>% 
  set_background_color(c(2),c(1), "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_opo %>% set_caption("")
```
Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$
\begin{equation*}
n=`r modlat$n_o[1]` \text{ , } m=`r modlat$m_o[1]`
\end{equation*}
\begin{equation*}
\xi=`r modlat$xi_o[1]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_o[1]`=`r modlat$Omega_o[2]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lamda_o[1]`=`r modlat$lamda_o[2]`
\end{equation*}

##

```{r, echo=F}
ctone_of <- 'Election results applying opposition form'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
kableExtra::kbl(format(stfo_sel,digits=4), caption=ctone_of) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

## `r metad$toc$sec1$unm[5]`

- **Step 1:** Each registered voter assign themself (independent of voting technology) to either candidate A or candidate B
- **Step 2:** Voting technology realized
- **Step 3:** Registered voters determine whether to vote or not to vote 
- **Step 4:** If voting, do this by either mode 1 or by mode 2.


```{mermaid}
  flowchart LR
  A[Candidate A or B] --> R[A]
  R --> RV[Vote]
  RV --> RVE[Non-Mail]
  RV --> RVM[Mail]
  R --> RN[Not Vote]
  DV --> DVE[Non-Mail]
  DV --> DVM[Mail]
  A --> D[B]
  D --> DV[Vote]
  D --> Dn[Not Vote]
```

##

- Probability of assigning oneself to candidate A in precinct $i$
  - $p_{w,i} \sim N(\alpha_i,\sigma^2_{w,i})$
- Voting technology
  - $z_i \sim U(0,1)$
- Probability of not voting in precinct $i$
  - Candidate A, $p_{nz,a,i}=(1-z_i)p_{n,a,i}\sim N(\alpha_{a,n},\sigma^2_{a,n})$ <br>
  - Candidate B, $p_{nz,b,i}=(1-z_i)p_{n,b,i}\sim N(\alpha_{b,n},\sigma^2_{b,n})$
- Probability of voting by mode 2 in precinct $i$
  - Candidate A, $p_{m2,a,i}=(1-p_{nv,a,i})p_{a,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
  - Candidate B, $p_{m2,b,i}=(1-p_{nv,b,i})p_{b,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
- Probability of voting by mode 1 in precinct $i$
  - Candidate A, $p_{m1,a,i}=1-p_{m2,a,i}-p_{nz,a,i}$ 
  - Candidate B, $p_{m1,b,i}=1-p_{m2,b,i}-p_{nz,b,i}$ 

Neutral-voting assumption:

- Decission to vote or not to vote is independent of voting preferences:
  - $p_{nz,a,i}=p_{nz,a,i}$ 
- If voting, decission to vote by mode 1 or by mode 2 independent of voting preferences: 
  - $p_{m2,a,i}=p_{m2,a,i}$ 

Note: As we will investigate later, this condition might be needed in order to restore a rigged election to its original form. 

## `r metad$toc$sec1$unm[6]`

1. Differences in the cost of voting (e.g., topology, voting rules, dropboxes etc.) across precincts $\Rightarrow$
1. Changes to the likelihood of voting $\Rightarrow$ 
1. Simplify so that changes in the likelihood of voting only impact Mode 2 $\Rightarrow$ 
1. Higher $\zeta_i$ $\Rightarrow$
1. Which changes the total election outcome through $\alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}$

##

The impact on the election outcome, however, would be small or close to non-existens if the conditions
of the existance of a *trivial* Manifold occuranse related to normal form are not satisfied:

- Proportion of mail-in-votes to election day vote is already high (Aggregate convergence lemma)
  - Note: $\lim_{\zeta_i \rightarrow \infty} \alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}=y_i$
- Correlation between $x$ and $y$ is very high (Twixt lemma)
  - Note: If correlation is 1, we can set $x_i=\rho_s y_i$ so that $\alpha_i(y_i,\zeta_i)=\frac{\rho_s y_i+\zeta_i y_i}{\zeta_i+x_i}$
- Low variance to $\zeta$ 
  - Note: Invariance across precincts would imply that $\zeta_i=\zeta$, so that election outcome only determined by variations in two parameters: $\alpha_i(y_i,x_i)=\frac{x_i+\zeta y_i}{\zeta+x_i}$
	
If none of this three cases are satisfied, variation in $\zeta_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?

## `r metad$toc$sec1$unm[7]`

1. Differenc in the cost of voting (e.g., topology, voting rules, dropboxes, socio economics etc.) across precincts $\Rightarrow$ 
1. Make changes to the likelihood of voting $\Rightarrow$ 
1. Simplify so that changes in the likelihood of voting only impact mode 2 $\Rightarrow$ 
1. Higher $\zeta_i$ $\Rightarrow$
1. If new and earlier sample not representative of each other, higher $\Gamma_i$ $\Rightarrow$
1. Which changes the total election outcome through $\alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+1}$

##

The impact on the election outcome, however, would be small or close to non-existens if the conditions
of the existance of a *trivial* Manifold related to opposition form are not satisfied:

- Proportion of the hybrid ballot boxes is already high (Aggregate convergence lemma)
  - Note: $\lim_{\Gamma_i \rightarrow \infty} \alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+g_i}=y_i$
- Correlation between $g$ and $h$ is very high (Twixt lemma)
  - Note: If correlation is 1, we can set $g_i=\rho_h h_i$ so that $\alpha_i(h_i,\Gamma_i)=\frac{\rho_h h_i+\Gamma_i h_i}{\Gamma_i+x_i}$
- Low variance to $\Gamma_i$ 
  - Note: Invariance across precincts would imply that $\Gamma_i=\Gamma$, so that election outcome only determined by variations in two parameters: $\alpha_i=\frac{g_i+\Gamma h_i}{h_i}$

If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?


# `r metad$toc$sec2$nmn`

## `r metad$toc$sec2$unm[1]`

- We have identified three ways of counting
  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
-  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
  -  We are free to *predetermine* **3** of them
  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
  -  Selecting **3** parameters from a set of **5** implies **10** different combinations

## `r metad$toc$sec2$unm[2]`


**20 laws and 40 isometris**

```{r, echo=F}
# Load necessary library
library(tibble)

# Create the data.frame
laws_df <- tribble(
  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
)
# Display the data.frame
kable(laws_df, format = "markdown", escape = FALSE)
```

##

::: {.callout-caution collapse="true"}
## Proportions

```{r, echo=F}
library(kableExtra)
library(tibble)
new_tbl <- data.frame(
  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
)

# Extract the columns
V1 <- new_tbl$V1
V2 <- new_tbl$V2
V3 <- new_tbl$V3
V4 <- new_tbl$V4
Equation1 <- new_tbl$Equation1
Equation2 <- new_tbl$Equation2
Equation3 <- new_tbl$Equation3
Equation4 <- new_tbl$Equation4

# Combine the columns
combined <- data.frame(
  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
)
kable(combined, format = "markdown", escape = FALSE)
```

:::

[@delfino2011analysis]

## `r metad$toc$sec2$unm[3]`

## `r metad$toc$sec2$unm[4]`

## `r metad$toc$sec2$unm[5]`

# `r metad$toc$sec3$nmn`

## `r metad$toc$sec3$unm[1]`

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_n_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_n_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_n_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_n_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_n_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_n_out[['resp']]
```

:::


## `r metad$toc$sec3$unm[2]`

**Example 1: Normal form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex1_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex1_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['resp']]
```

:::


##

**Example 2: applying hybrid form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex2_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex2_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['resp']]
```

:::



##

**Example 3: applying opposition form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex3_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex3_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['resp']]
```

:::


# `r metad$toc$sec4$nmn` {#litrev}


```{r, echo=FALSE, out.width="20%", fig.cap=""}
p1 <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/ss.png')
knitr::include_graphics(c(p1))
```

`r #Citet(bib, "delfino2011analysis")`

> Abstract: On August 15th, **2004**, Venezuelans had the opportunity to vote
in a Presidential Recall Referendum **to decide whether or not President Hugo
Chávez should be removed from office.** **The process was largely computer-
ized using a touch-screen system.** In general the ballots were not manually
counted. The significance of the high linear correlation (0.99) between the
number of requesting signatures for the recall petition and the number of op-
position votes in computerized centers is analyzed. The same-day audit was
found to be not only ineffective but a source of suspicion... 

::: aside
[Link to Youtube-video](https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s)
:::

##

- Venezuela referendum to recall President Hugo Chávez (2004)
	- Mode 1: Computerized Voting Centers
	- Mode 2: Manuel Voting Centers

> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.

```{r, echo=FALSE, out.width="85%", fig.cap=""}
p3 <- paste0(rprojroot::find_rstudio_root_file(),'pngs/manifold.png')
knitr::include_graphics(c(p3))
```

# `r metad$toc$sec5$nmn` {#proced}

# `r metad$toc$sec5$unm[1]` 

1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
1. Check for normality of the estimated residual for the Manifold model.

If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.

# `r metad$toc$sec6$nmn`


```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="1")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```


```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```


# `r metad$toc$sec7$nmn`

- At the heart of the difference between a fair and rigged election is the issue of causation
  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate

- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.

##

- Condition on that $R^2$ falls within the critical region.
  - Normal form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2n.png')
knitr::include_graphics(c(pr2n))
```

 - Hybrid form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2h.png')
knitr::include_graphics(c(pr2h))
```



- Our four applications

```{r, echo=F, warning=F, message=F}
#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

# `r metad$toc$sec8$nmn`

::: {#refs}
:::




