---
title: "Addendum"
subtitle: "Arizona General Election 2022"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "abc.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
#output:
#  html_document:
#    toc: true
#    toc_depth: 5
---

```{r, echo=F, warning=F, message=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
library(plotly)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_tile_view()
xaringanExtra::use_share_again()
xaringanExtra::use_scribble()
xaringanExtra::use_webcam()
xaringanExtra::use_panelset()
modlat <- eqpar$meql
labs <- stickers[['parameters']]
abs_p <- rprojroot::find_rstudio_root_file()
#source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_az.R'))
```

```{r, eval=F, echo=F, message=F, warning=F}
pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/inst/www/addendum/Addendum_az.Rmd')
xaringan::inf_mr(pre_fil)
#rmarkdown::render(pre_fil) 
```

```{r}
knitr::knit_exit()
```

class: inverse, center, middle

# Overview

```{r, echo=FALSE, out.width="80%", fig.cap=""}
pa <- paste0(rprojroot::find_rstudio_root_file(),'/inst/addendum/pngs/ALEXANDER_chart-of-Rs-voting-for-Hobbs.jpg')
knitr::include_graphics(c(pa))
```

---

class: inverse, center, middle

# Maricopa county

---

## [Application 1:`r paste0(unlist(ManifoldDestiny::cap_add_mar[1])[1:3])`]()

- Election system:
  - General election 2022
  - Modes of voting: EDV, (used) MiV (used), EV (used)

- $H_0:$ Normal election 
  - $y_i(\alpha_i,x_i.\zeta_i)$
  - Variation in $\zeta_i$ causes changes to $\alpha_i$

- $H_1:$ Rigged election applying opposition form
  - $y_i(\alpha_i,x_i)=M(x_i,\alpha_i)+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
  - $\zeta_i$ (and as a corollary $\Omega$) invariant to $\alpha_i$

---

.panelset[
.panel[.panel-name[Descriptive]
```{r, echo=F}
format(app_ma_sen_srp[[1]][,1:6],digits=10)
format(app_ma_sen_srp[[1]][,7:18],digits=4)
```
]
.panel[.panel-name[2d plots]
```{r, echo=F}
app_ma_sen_srp[[2]]
```
]
.panel[.panel-name[3d plot]
```{r, echo=F}
app_ma_sen_srp[[3]]
```
]
.panel[.panel-name[Estimation results]
```{r, echo=F}
app_ma_sen_srp[[4]][2]
```
]
.panel[.panel-name[Residuals]
```{r, echo=F}
app_ma_sen_srp[[5]]
```
]]

---


```{r, echo=F, out.width="80%", fig.cap=""}
td
```

---

![](ggplots/prec/race_1_snap)

---

---

![](ggplots/prec/race_2_snap)

---


```{r, echo=F, out.width="80%", fig.cap=""}
kableExtra::kbl(snap_mar$rpoltab,col.names=c("Race","Snap","Polynomial","Integral","R2")) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
```

---

class: inverse, center, middle

# Cohise county

---

## [Application 2:`r paste0(unlist(ManifoldDestiny::cap_add_coh[2][1:3])[1:2])`]()

- Election system
  - General election 2022
  - Modes of voting: EDV, (used) MiV (used), EV (used)

- $H_0:$ Normal election 
  - $y_i(\alpha_i,x_i.\zeta_i)$
  - Variation in $\zeta_i$ causes changes to $\alpha_i$

- $H_1:$ Rigged election applying opposition form
  - $y_i(\alpha_i,x_i)=M(x_i,\alpha_i)+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
  - $\zeta_i$ (and as a corollary $\Omega$) invariant to $\alpha_i$

---


.panelset[
.panel[.panel-name[Descriptive]
```{r, echo=F}
format(app_co_sen_srp[[1]][,1:6],digits=10)
format(app_co_sen_srp[[1]][,7:18],digits=4)
```
]
.panel[.panel-name[2d plots]
```{r, echo=F}
app_co_sen_srp[[2]]
```
]
.panel[.panel-name[3d plot]
```{r, echo=F}
app_co_sen_srp[[3]]
```
]
.panel[.panel-name[Estimation results]
```{r, echo=F}
app_co_sen_srp[[4]][2]
```
]
.panel[.panel-name[Residuals]
```{r, echo=F}
app_co_sen_srp[[5]]
```
]]

---

```{r, echo=F, out.width="80%", fig.cap=""}
plo_sta_all
```

---

```{r, echo=F, out.width="80%", fig.cap=""}
kableExtra::kbl(sna_sta_all$rpoltab,col.names=c("Race","Snap","Polynomial","Integral","R2")) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
```

